---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "Readme_files/"
)

devtools::load_all()
```

# Base Predict Function for DataSHIELD

## Overview

## Installation

#### Developer version:

The package is currently hosted at a private GitLab repository. If access is granted, the installation can be done via `devtools`:

```r
cred = git2r::cred_user_pass(username = "username", password = "password")
devtools::install_git("https://gitlab.lrz.de/difuture_analysegruppe/ds.predict.base.git", credentials = cred)
```

Note that you have to supply your username and password from GitLab to install the package.

#### Register assign methods

It is necessary to register the assign methods in the OPAL administration to use them. The assign methods are (with namespaces):

- `ds.predict.base::decodeModel`
- `ds.predict.base::assignPredictModel`

## Usage

The following code shows the basic methods and how to use them. Note that this package is intended for internal usage and base for the other packages and does not really have any practical usage for the analyst.

```{r, results="hide", warnings=FALSE}
library(DSI)
library(DSOpal)
library(DSLite)
library(dsBaseClient)

# library(ds.predict.base)

builder = DSI::newDSLoginBuilder()

builder$append(
  server   = "ibe",
  url      = "https://dsibe.ibe.med.uni-muenchen.de",
  user     = "ibe",
  password = "123456",
  table    = "ProVal.KUM"
)

logindata = builder$build()
connections = DSI::datashield.login(logins = logindata, assign = TRUE, symbol = "D", opts = list(ssl_verifyhost = 0, ssl_verifypeer=0))

### Get available tables:
DSI::datashield.symbols(connections)

### Test data with same structure as data on test server:
dat   = cbind(age = sample(20:100, 100L, TRUE), height = runif(100L, 150, 220))
probs = 1 / (1 + exp(-as.numeric(dat %*% c(-3, 1))))
dat   = data.frame(gender = rbinom(100L, 1L, probs), dat)

### Model we want to upload:
mod = glm(gender ~ age + height, family = "binomial", data = dat)

### Upload model to DataSHIELD server
pushModel(connections, mod)

# Check if model "mod" is now available:
DSI::datashield.symbols(connections)

# Check class of uploaded "mod"
ds.class("mod")

# Now predict on uploaded model and data set D:
predictModel(connections, mod, "pred", dat_name = "D")

# Check if prediction "pred" is now available:
DSI::datashield.symbols(connections)

# Summary of "pred":
ds.summary("pred")

# Now assign values with response type "response":
predictModel(connections, mod, "pred", "D", predict_fun = "predict(mod, newdata = D, type = 'response')")

ds.summary("pred")
```

